Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-22 paper/ms.tex
update manuscript

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS lightcurve of \tn\ (Sectors 10 and 11).}
    {\it Top}: \texttt{PDCSAP} median-subtracted relative flux at
    2-minute sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Spot-induced stellar variability is the
    dominant signal.  Dashed lines show the five transits observed by
    TESS.
    {\it Bottom}: Zoomed windows of individual transits.  Red points
    highlight manually identified stellar flares.
		\label{fig:rawzoom}
	}
\end{figure*}

@@

@@

\tn\ (GAIA DR2 5251470948229949568) was observed by the
TESS spacecraft from X to Y in two-minute cadence mode.
The star was designated
TIC\,460205581 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.
%FIXME make words more original
The pixel data for an
$11\times11$ array surrounding \tn\ were averaged into 2-minute
stacks by the onboard computer.  Each 2048$\times$2048 image from the
CCD was also averaged into 30-minute stacks, and saved as a ``full
frame image'' (FFI).

%FIXME make words more original
The pixel data for an
The 2-minute stacks for \tn\ were reduced to lightcurves by the
Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
Conditioning (PDC) lightcurve.  The PDC lightcurve aperture used
pixels chosen to maximize the SNR of the total flux of the target
\citep{smith_finding_2016}.  Non-astrophysical variability
was removed by fitting out trends common to many stars
\citep{smith_kepler_2012,stumpe_multiscale_2014}.

%FIXME make words more original
As an independent check on the 2-minute SPOC lightcurve, we examined
the lightcurve based upon 30-minute image stacks which was produced as
part of the Cluster Difference Imaging Photometric Survey (CDIPS;
\citealt{bouma_cluster_2019}).  Our CDIPS lightcurve of choice used a
circular aperture with radius 1 pixel.

%TODO: describe 0.3-day robust Huber spline

Figure~\ref{fig:rawzoom}.

\subsection{Ground-based Time-Series Photometry}
\label{subsec:groundphot}

\subsection{Imaging}

\subsection{Spectroscopy}

@@

\subsection{Astrometry}

@@

\subsubsection{Gaia Imaging}
Figure~\ref{fig:scene} shows the scene as viewed in the DSS2 plates
and by TESS.  In the upper panels, the pixels used to measure the
background level in the SPOC lightcurve are indicated with
`\texttt{X}' hatching, and the pixels used in the final lightcurve
aperture are shown with `\texttt{/}' hatching.

Stars brighter than $T=16$, as queried from the Gaia DR2 source
catalog, are shown with orange circles.  Given its galactic latitude
of $b=-6^\circ$, it is not surprising that the field of \tn\ is
crowded.  The stars that were of immediate concern for a blend
analysis were as follows.
\begin{itemize}
  \item \tn\ = TIC 460205581 (T=9.9). The target star.
  \item Star A = TIC 847769574 (T=14.6). $2.3$'' west. Proper motions
    and parallax imply it is comoving with \tn, though with a physical
    separation of $6.6\pm 0.1\,{\rm pc}$, it may not be bound.
  \item Star B = TIC 460205587 (T=13.1). $5.4$'' north.  This is a
    giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9$'' from the target, but
too faint (T=18.8) to be the source of the observed transit signal.

The Gaia DR2 data for Star A seems poorly behaved.  While
Star A has $G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
Correspondingly, no RUWE value is available (CITE).  The astrometric
reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number of good
astrometric observations) seems rather poor, at $8.6$.  We suspect
that the photometric failure to produce an $Rp$ magnitude, as well as
the poor astrometric fit, are likely due to blending with \tn.

At the angular resolution of the TESS data, if either Star A or Star B
were eclipsing binaries, they could be the sources of the transit
signal.  We ruled out both Star A and Star B as hosts of the eclipse
through a detailed analysis of the ground-based seeing-limited
photometry (\S~\ref{subsec:groundphot}).

@@

Additional point-sources could be present beyond the angular
resolution of the Gaia source catalog.
To limit this possibility,
we imaged the system using SOAR-HRCam, as described in
\citet{ziegler_soar_2020}.
{\bf Carl: please describe}.
The bandpass was a Johnson-Cousins,
where I is centered at 879 nm and has a width of 289 nm.

Figure~\ref{fig:soar} shows the result.
Star A (TIC 847769574) is detected as expected, and no additional
companions are found.
"""
The points on the plot are measured 5-sigma detectable contrasts. The
lines are linear smoothing fits between two regimes. In general, the
sensitivity of speckle imaging to companions rises sharply from the
diffraction limit to a ``knee'' at a separation of 0.15--0.2
arcseconds, where it then continues to slowly increase out to 1.5$''$,
beyond which the speckle patterns become de-correlated. For this
target, I suspect the measurement at 1$''$ is slightly larger than
expected due to some increase in speckle noise at that radius.
"""

@@

\subsubsection{TESS}
We examined the CDIPS FFI lightcurves of the target, which are
available on MAST \citep{bouma_cluster_2019}. Three lightcurves are
available, based on photometric apertures with a radius of 1, 1.5, or
2.5 pixels.  In the raw difference-image light-curves, as well as the
PCA-detrended light-curves, dips of depth $\approx$0.35\% are visible,
and their properties do not significantly vary with aperture size.
Within $\approx20$'', the dips are consistent with originating from
the target star.

@@

To assess this possibility with the ground-based photometry, we
produced lightcurves centered on \tn\ with
circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
We did not detect any statistically significant variation in the depth
of the transits.

We also created lightcurves with a custom set of $r=2.1''$ apertures
with positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
east of \tn.  We did not detect any variation of the transit depth
along this line of lightcurves, as would be expected if Star A were
the eclipse host.  The apertures east of \tn\ are particularly
constraining, as they exclude over 90\% of the flux from Star A.
The eclipse on Star A would therefore need to be excessively deep to
produce the observed eclipse depth.
We take this to indicate that \tn\ is the source of the transit signal
to within $\approx2.0''$.

@@

@@

\acknowledgements
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank...
%
We also thank the Heising-Simons Foundation for
their generous support of this work.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
This research made use of the Exoplanet Follow-up Observation
Program website, which is operated by the California Institute of
Technology, under contract with the National Aeronautics and Space
Administration under the Exoplanet Exploration Program.
%
This research has made use of the SVO Filter Profile Service
(\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
MINECO through grant AYA2017-84089
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019}
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:agol19}
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano}.
  \texttt{IPython} \citep{perez_2007},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}

>>>>

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Spot-induced stellar variability is the dominant signal.  Dashed
    lines show the five transits observed by TESS.  {\it Bottom}:
    Zoomed windows of individual transits.  Red points are manually
    identified stellar flares.
		\label{fig:rawzoom}
	}
\end{figure*}

@@

\tn\ was observed by TESS from 26 March 2019 until 20 May 2019, during
the tenth and eleventh sectors of science operations
\citep{ricker_transiting_2015}.  The star was designated
TIC\,460205581 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.  Pixel data for an
$11\times11$ array surrounding the star were averaged and saved at
2-minute cadence.  The $2048\times2048$ image from the entire CCD was
also averaged into 30-minute stacks, and saved as a ``full frame
image'' (FFI).

The TESS project detected the transits in the 2-minute data and the
community was alerted on 17 June 2019.  While our CDIPS FFI light
curves also show the transits, the 2-minute data have better sampling
cadence, and so we opted to use the Presearch Data Conditioning (PDC)
light curve with the default aperture for our
analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,jenkins_tess_2016,smith_finding_2016}.

Figure~\ref{fig:rawzoom} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips
suggestive of a grazing transiting planet recur roughly every 8 days,
and have a depth of about 0.4\%.  A few flares are visible.  A
phase-folded version of the TESS transits with starspot variability
removed is shown in Figure~\ref{fig:jointphot}, and is described in
depth in Section~\ref{subsec:planet}.

\subsection{Gaia Astrometry and Imaging}
\label{subsec:gaia}

Between 25 July 2014 and 23 May 2016, the ESA Gaia satellite measured
about 300 billion centroid positions of 1{.}6 billion stars.  The
positions, proper motions, and parallaxes of the brighest 1{.}3
billion were calculated for the second data release (DR2)
\citep{gaia_collaboration_gaia_2016,lindegren_gaiasoln_2018,gaia_collaboration_gaia_2018}.
\tn\ was assigned the Gaia DR2 identifier 5251470948229949568, and had
276 ``good'' astrometric observations. Its brightness was measured in
the $G$, $Rp$, and $Bp$ bands of the Radial Velocity Spectrometer
\citep{cropper_gaia_2018,evans_gaia_2018}.

The Gaia imaging, as represented by its point-source catalog, provides
the initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
orange circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
not surprising that the field of \tn\ is crowded.  The stars that were
of immediate concern for our false positive analysis were as follows.
\begin{itemize}
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
    proper motions and parallax of this star imply it is comoving with
    \tn, though with a physical separation of $6.6\pm 0.1\,{\rm pc}$,
    it may not be bound.
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9$'' from the target, but
too faint (T=18.8) to be the source of the observed transit signal.

The Gaia DR2 data for Star A seems poorly behaved.  While
Star A has $G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
Correspondingly, no RUWE\footnote{ See the Gaia
DPAC technical note GAIA-C3-TN-LU-LL-124-01,
\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
2020-06-22. } value is available.  The astrometric
reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number of good
astrometric observations) seems rather poor, at $8.6$.  We suspect
that the photometric failure to produce an $Rp$ magnitude, as well as
the poor astrometric fit, are likely due to blending with \tn.

At the $\approx1'$ resolution of the TESS data, if either Star A
or Star B were eclipsing binaries, they could be the sources of the
transit signal.  A detailed analysis of ground-based seeing-limited
photometry was necessary to assess and rule out this possibility
(Section~\ref{subsec:groundphot}).

\subsection{High-Resolution Imaging}
\label{subsec:speckle}

To determine if any fainter point sources existed closer to \tn\
inside of Gaia's point-source detection limits, we acquired
high-resolution speckle images. We then searched the autocorrelation
functions of these images for peaks indicative of nearby companions.

{\bf Carl TODO: please describe and correct as appropriate}
The observations of \tn\ were initially acquired by
\citet{ziegler_soar_2020} as part of the Southern Astrophysical
Research (SOAR) TESS Survey using the High Resolution Camera (HRCam;
\citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:soar}
show the resulting measured 5-$\sigma$ detectable contrasts.  The
lines are linear smoothing fits between the regimes of the diffraction
limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
$\approx 1.5''$, beyond which the speckle patterns become
de-correlated.  Star A (TIC 847769574) was detected at the expected
location and brightness contrast, and no additional companions were
found.

\subsection{Ground-based Time-Series Photometric Follow-up}
\label{subsec:groundphot}

We obtained ground-based seeing-limited time series photometric
observations of \tn\ bracketed around the times of transit.  These
observations confirmed that the transits occurred on-target to within
$\approx 2''$, and that they were achromatic. Both features are
essential for our ability to eliminate false-positive scenarios.

\subsubsection{El Sauce 0.36m}

We observed four transits with the 0.36m at Observatario El Sauce,
located in the R\'io Hurtado Valley in Chile, and operated by
co-author P{.}~Evans.  The observations were obtained in Cousins-R
band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
on the night of 21 May 2020, and Johnson-B band on the night of 14
June 2020.  The final 14 June transit began shortly after twilight.

{\bf Phil + Karen TODO: please correct as appropriate}
We scheduled the observations using {\bf \texttt{SOFTWARE}} (CITE).
The photometric data were calibrated and extracted using the
\texttt{AstroImageJ} software package
\citep{collins_astroimagej_2017}.  Comparison stars of similar
brightness were used to produce the final light curves, each of which
showed a roughly 4$\,$ppt dip near the expected transit time.
We produced and examined light curves with at custom positions and
with custom aperture sizes, and...

The data were reduced using... (e.g., astroimageJ)

{\bf LGB TODO: Describe custom analysis of apertures}

\subsubsection{ASTEP400}

{\bf Amaury TODO: please correct as appropriate}
We observed {\bf N} transits with the 0.40m ASTEP 400 telescope at
Concordia Station, located at Dome C on the Antarctic Plateau
\citep{daban_astep_2010}.  ASTEP 400 has a dichroic that sends blue
wavelengths to a guiding camera, and red wavelengths to a filter-free
science camera with wavelength sensitivity roughly akin to R band.
The observations were acquired on the nights of {\bf DATE 1} and {\bf
DATE 2}.  The outdoor temperature was a balmy {\bf XX$^\circ$}.  The
data were reduced using {\bf XX} software, and showed the transit
roughly at the expected time and depth.

\subsection{Spectroscopic Follow-up}
\label{subsec:spectra}

@@

@@

@@

\subsubsection{Gaia Imaging}
{\it empty}

@@

@@

\subsubsection{TESS}
We examined the CDIPS FFI light curves of the target, which are
available on MAST \citep{bouma_cluster_2019}. Three light curves are
available, based on photometric apertures with a radius of 1, 1.5, or
2.5 pixels.  In the raw difference-image light-curves, as well as the
PCA-detrended light-curves, dips of depth $\approx$0.35\% are visible,
and their properties do not significantly vary with aperture size.
Within $\approx20$'', the dips are consistent with originating from
the target star.

@@

To assess this possibility with the ground-based photometry, we
produced light curves centered on \tn\ with
circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
We did not detect any statistically significant variation in the depth
of the transits.

We also created light curves with a custom set of $r=2.1''$ apertures
with positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
east of \tn.  We did not detect any variation of the transit depth
along this line of light curves, as would be expected if Star A were
the eclipse host.  The apertures east of \tn\ are particularly
constraining, as they exclude over 90\% of the flux from Star A.
The eclipse on Star A would therefore need to be excessively deep to
produce the observed eclipse depth.
We take this to indicate that \tn\ is the source of the transit signal
to within $\approx2.0''$.

@@

%TODO: describe 0.3-day robust Huber spline (or whatever detrending is
%eventually used)

@@

\acknowledgements
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank...
%
We also thank the Heising-Simons Foundation for
their generous support of this work.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
This research made use of the Exoplanet Follow-up Observation
Program website, which is operated by the California Institute of
Technology, under contract with the National Aeronautics and Space
Administration under the Exoplanet Exploration Program.
%
This research has made use of the SVO Filter Profile Service
(\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
MINECO through grant AYA2017-84089
%
\tn\ was included on the TESS ``short-cadence'' target list in part
thanks to the Guest Investigator program of G.\ Sacco (G011265).

%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019}
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:agol19}
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano}.
  \texttt{IPython} \citep{perez_2007},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
